%===============================================================================
% File Name     : dolphin-di-faqs.txt
% File Created  : 2025-10-04 10:16 UTC +02:00
% Description   : Frequently Asked Questions about Dolphin Design Intelligence
%-------------------------------------------------------------------------------
% Author        : Amit Manohar Manthanwar
% Website       : https://manthanwar.github.io
%-------------------------------------------------------------------------------
% Copyright     : ©2025 Amit Manohar Manthanwar
% License       : LaTeX Project Public License
%-------------------------------------------------------------------------------
% This program can be redistributed and/or modified under the terms
% of the LaTeX Project Public License Distributed from CTAN archives
% in directory macros/latex/base/lppl.txt.
%---------------+---------+-----------------------------------------------------
% Authorised File Editors
% AMM = Amit Manohar Manthanwar
% PCM = Purna Chanra Mohan
%-------------------------------------------------------------------------------
% Revision Log  | Author  | Description
%---------------+---------+-----------------------------------------------------
% 04-Oct-2025   | AMM     | Initial Version
%---------------+---------+-----------------------------------------------------
%===============================================================================
% \section{Product Overview}
% \section{Features and Capabilities}
% \section{Ease of Use and Adoption}
% \section{Templates and Design}
% \section{Deployment and Setup}
% \section{Integration and Data Handling}
% \section{Security and Compliance}
% \section{Pricing and Licensing}
% \section{Troubleshooting and Support}
% \section{Feature Requests or Suggestions}
% \section{Ask Us Any Other Questions}
%===============================================================================
\section*{Most FAQs by First-time Users}
\question{What is Dolphin Design Intelligence?}
\answer{Dolphin is your all-in-one platform for documents and design needs. It instantly generates a variety of document formats including letters, reports, proposals, presentations, certificates, invoices, infographics, and many more types---directly from your data. Instead of juggling Word, PPT, PDF, and other design tools, Dolphin gives you a unified workspace with consistent, highest-resolution print-ready, professional outputs while keeping the file sizes at their lowest.}

\question{How does Dolphin serve as a one-stop shop for my design and documentation?}
\answer{Teams usually spend hours formatting in Word, designing in PowerPoint, or exporting to PDF. Dolphin eliminates this complexity. Using data-driven smart templates, it automates repetitive tasks and instantly creates high-quality outputs---saving time, ensuring brand consistency, and delivering faster results.}

\question{Is it easy to use?}
\answer{Yes. If your team can use Word or Excel, they can use Dolphin. The learning curve is minimal, and we provide onboarding support and training to get you started quickly.}

\question{How fast is it?}
\answer{Instant. Whether it's 10 or 10,000 documents, Dolphin generates outputs in seconds once the template and data are ready.}

\question{How much does it cost?}
\answer{Pricing depends on your team size and usage. We offer both subscription-based and perpetual license options, with flexibility for different organizations.}

\question{Is Dolphin cloud-based or on-premises?}
\answer{Both. By default, Dolphin is cloud-based for convenience, but we also support on-premises deployment for organizations with strict security or compliance needs.}

%===============================================================================
\section{Product Overview}

\question{What types of documents can Dolphin generate automatically?}
\answer{Dolphin generates a wide range of outputs, including vector art designs, reports, proposals, presentations, certificates, invoices, business cards, brochures, catalogs, certificates, and marketing materials---all instantly from your data. See our product offerings to learn more. We can also develop customized solution to your needs.}

\question{My employees are accustomed to Word, PPT, and PDF. Why should we learn Dolphin?}
\answer{Dolphin directly addresses the biggest pain points these tools can't solve---like manual formatting and repetitive document tasks. Instead of spending hours, you simply supply your data, pick a template, and Dolphin instantly generates professional, high-quality documents. The learning curve is minimal, and productivity gains are significant.}

\question{Will Dolphin add to the long list of tools we already use?}
\answer{No. Dolphin actually reduces tool overload. Instead of juggling Word, Adobe, PowerPoint, and multiple design tools, Dolphin provides a single platform for all your needs---reports, invoices, certificates, presentations, brochures, and more---in one clean, easy-to-use workspace.}

\question{Does it take a lot of effort to create templates?}
\answer{Template creation is a one-time activity handled by our design team according to your brand guidelines. Once ready, templates can be reused indefinitely and can be easily reconfigured by anyone with authorization. Dolphin also provides a library of pre-made, stunning templates---just choose one, supply your data, and get instant results.}

%===============================================================================
\section{Features and Capabilities}

\question{Can Dolphin handle bulk jobs like certificates, invoices, or ID cards?}
\answer{Yes. Whether it's 10 or 10,000 documents, Dolphin generates them instantly, optimized for print, screen, and other media formats while maintaining consistent quality.}

\question{Can Dolphin convert static designs into dynamic, configurable templates for experimentation and customization?}
\answer{Yes. Dolphin allows you to transform static designs into dynamic, parameter-driven templates that adapt automatically to your data. These templates can be reused or modified easily, enabling rapid experimentation, personalization, and bulk generation of high-quality outputs for both digital and print formats.}

\question{How does Dolphin ensure high-quality outputs with minimal file sizes?}
\answer{Dolphin uses vector-based design intelligence and optimized algorithms to maintain professional quality while keeping files lightweight---suitable for both digital and print applications.}

%===============================================================================
\section{Ease of Use and Adoption}

\question{Is Dolphin easy to use for non-technical employees?}
\answer{Yes. If your team can use Word or Excel, they can use Dolphin. Even if they cannot they still can lean to use Dolhin quickly and with ease. Data input is simple via raw CSV or Excel dump and the platform handles the rest automatically.}

\question{Do you provide training or onboarding support?}
\answer{Yes. We offer both online and onsite training to bring your team up to speed quickly and ensure smooth adoption.}

\question{What data formats are supported?}
\answer{Dolphin supports CSV, Excel, JSON, plain text, and direct database connections for seamless integration with your existing systems.}

%===============================================================================
\section{Templates and Design}
\def\colorQed{teal!50}%

\question{How are templates created? Does Dolphin provide pre-designed templates?}
\answer{Templates are created upfront based on your brand and design requirements. Dolphin also provides pre-made, professional templates that you can customize and reuse.}

\question{Can Dolphin match my brand guidelines and style requirements?}
\answer{Yes. Templates and outputs can be tailored to your brand colors, fonts, logos, and visual style, ensuring professional and consistent presentation.}

%===============================================================================
\section{Deployment and Setup}

\question{Is Dolphin available on cloud or on-premises?}
\answer{Dolphin is primarily cloud-based, but on-premises deployment is also available for organizations with local data requirements.}

\question{What do I need to install or configure before using Dolphin?}
\answer{Minimal setup is needed. Access is via a web browser or lightweight client, and your team only needs to provide data and select templates. No complex installations or any other third party software are required.}

%===============================================================================
\section{Integration and Data Handling}

\question{Can Dolphin integrate with my ERP or other internal systems?}
\answer{Yes. Dolphin connects via APIs or direct database access, allowing you to fetch data automatically from your existing systems.}

\question{How does Dolphin handle data for report and document generation? Where is my data stored, and how is it set up?}
\answer{Your data can remain in your internal systems or be uploaded to Dolphin securely. Data is used only for generating outputs and is protected with strict security protocols. The template $\rightarrow$ data mapping is a simple setup step requiring no efforts.}

\question{How does Dolphin integrate with existing workflows or automation pipelines?}
\answer{Dolphin can be embedded into existing business processes via APIs or connectors, allowing automated document generation as part of your workflow.}

%===============================================================================
\section{Security and Compliance}
\def\colorQed{Purple!50}%

\question{Where will my data be stored, and how is it protected?}
\answer{Your data is stored in secure cloud servers or on-premises as per your requirements. Dolphin's data encryption, access controls, and secure protocols ensure protection against unauthorized access.}

\question{How is PII or sensitive data handled?}
\answer{Sensitive data is processed according to compliance standards, with encryption and restricted access to safeguard privacy.}

\question{Can Dolphin meet local data residency requirements?}
\answer{Yes. We offer data residency options based on your regulatory and geographic requirements.}

%===============================================================================
\section{Pricing and Licensing}

\question{What is Dolphin's pricing model? Is it subscription-based or a perpetual license?}
\answer{Dolphin offers both subscription-based and perpetual license options, depending on your needs.}

\question{Are there any volume, educational, or nonprofit discounts available?}
\answer{Yes. Discounted pricing is available based on volume, educational institutions, and nonprofit organizations.}

%===============================================================================
\section{Troubleshooting and Support}

\question{Who do I contact if I face issues?}
\answer{Our support team is available via email, chat, for prompt assistance.}

\question{How quickly is support available?}
\answer{Response times are fast, with SLA-based support for enterprise clients and quick resolution for general users.}

\question{Can I revert to previous template versions or outputs?}
\answer{Yes. Dolphin maintains version history for templates and generated documents.}

\question{How do I handle errors in data input or template setup?}
\answer{Dolphin provides error messages, data validation, and guided correction workflows to quickly fix issues.}

%===============================================================================
\section{Feature Requests or Suggestions}
\def\colorQed{Maroon!50}%

\question{Can I request a new feature or functionality?}
\answer{Yes. Users can submit requests via our feature request portal.}

\question{How do you prioritize user requests?}
\answer{Requests are prioritized based on user impact, feasibility, and strategic roadmap.}

\question{Will requested features be rolled out in updates?}
\answer{Yes. Approved requests are included in regular product updates and communicated to users.}

%===============================================================================
\section{Any Other Questions - Ask Us}

\question{If my question isn't listed here, how do I get an answer?}
\answer{You can submit your question through our support portal, and it will be answered promptly.}

\question{Can I submit my use case for personalized guidance?}
\answer{Yes. Our team reviews use cases and provides tailored solutions for your workflow and document needs.}

\question{How do I suggest improvements or provide feedback?}
\answer{Feedback can be submitted via our portal, and it is reviewed by the product and design teams for continuous improvement.}

